Dendro review

### 2018-04-17 analysis/analysis_age_elevation.Rmd
add new data

elev_age <- ggplot(df, aes(x=elev, y=length)) + 
  # geom_smooth(data = subset(df, elev > 500), se=FALSE, method = 'lm', colour="gray") +
  geom_point(size = 3, colour = "black") + theme_bw() + theme(panel.grid = element_blank()) + 
  geom_text_repel(data = subset(df, refs %in% c("1","2","3","4","5","6","7","8")), size = 3, aes(label=refs)) +
  geom_label_repel(data = subset(df, refs %in% c("SJ","CA-High", "CA-Low")), 
                   size = 5, aes(label=refs),
                   box.padding = 0.25, point.padding = 0.3) +
  xlab('Elevation (m)') + ylab('Age (years)') +
  ylim(0,350)

elev_age + annotation_custom(ggplotGrob(s), xmin = 0, xmax = 1400, ymin = 160)
# elev_age <- ggMarginal(elev_age, margins="y")
```

```{r}
ggplot(df, aes(length)) + geom_density()
```

>>>>

elev_age <- ggplot(df, aes(x=elev, y=length)) + 
  geom_smooth(data = subset(df, elev > 500), se=FALSE, method = 'lm', colour="gray") +
  geom_point(size = 3, colour = "black") + theme_bw() + theme(panel.grid = element_blank()) + 
  geom_text_repel(data = subset(df, !(refs %in% c("SJ","CA-High", "CA-Low"))), size = 3, aes(label=refs)) +
  geom_label_repel(data = subset(df, refs %in% c("SJ","CA-High", "CA-Low")), 
                   size = 5, aes(label=refs),
                   box.padding = 0.25, point.padding = 0.3) +
  xlab('Elevation (m)') + ylab('Age (years)') +
  ylim(0,350)

elev_age + annotation_custom(ggplotGrob(s), xmin = 0, xmax = 1400, ymin = 160)

```

```{r}
ggplot(df, aes(length)) + geom_density()

dff <- subset(df, elev > 500)

summary(lm(elev~length, data=dff))
```
